Covid-19 Fields Survey Data Protocol

### 2023-01-23 protocol/Background_and_methods_Jan_12.qmd
Idea on changing data to run analysis

@@

@@

Health_Regions<-data.frame(Health_Region=c(
  "North West",
  "North East",
  "West",
  "East",
  "Central",
  "Toronto"),
  Freq=c(232299,
    557000,
    4000000,
    3700000,
    5000000,
    1400000
  )
)

>>>>

clean_data <-clean_data %>%
  filter(Health_Region !="North East", Health_Region !="North West")

@@

clean_data %>%
  tbl_summary(
    include=c(
    Health_Region,)
  ) %>% bold_labels()

@@

Health_Regions<-data.frame(Health_Region=c(
  #"North West",
  #"North East",
  "West",
  "East",
  "Central",
  "Toronto"),
  Freq=c(#232299,
    #557000,
    4000000,
    3700000,
    5000000,
    1400000
  )
)

# probably best strategy is to remove the North West and North East regions as they only constitute 5% of the total population of Ontario.
